Region-network sparsity priors for\\ high-dimensional inference in fMRI data

### 2015-12-08 paper/paper.tex
last

structured sparsity
extend trend in stastical modelling from
genetics \cite{rapaport2008classification, kim2012tree},
natural image processing \cite{harzallah2009combining}

@@

integrative processes

@@

@@

If meaningful structures exist,
ÇÇçwe show that one can take advantage of such structures

@@

@@

@@

@@

@@

>>>>

structured sparsity
extend trend in stastical modelling from
processing of auditory signals \cite{daudet2004sparse},
natural images \cite{harzallah2009combining} and
videos \cite{kang2015structured, kim2010sparse}
to
genetics \cite{rapaport2008classification, kim2012tree}
and
conformational dynamics of protein complexes \cite{jenatton2009structured}.

tructured-sparsity-inducing penalty

@@

imposing parsimony
integrative processes

@@

representing some phenomenon with as few variables as possible

@@

If meaningful structures exist,
we show that one can take advantage of such structures

Statistically,
l1 and l2 are local sparsity priors
-> resulting sparsity does yield structure
we want to priviledge representations with structure

=> 
 a biologically and statistically desirable bias

@@

Group-sparsity is a first step towards the more general idea that
a regularization function can encourage sparse solutions with a particular structure.

@@

groups at multiple granularity

tree-guided group lasso

encourage structured shrinkage effect

@@

Our method extends the L1/L2 penalty to the tree-lasso penalty
by letting the hierarchically-defined groups overlap. 
the tree lasso is a special case of overlapping group lasso

@@

Among a collection of plausible models,
the simplest one should be preferred

@@

Differences to Bertrands structured sparsity paper:
- they derive the tree from the data, we use a priori knowledge from
the existing literature
-
